Multimatrices and Their Derivatives

### 2019-05-17 Math/paper.tex
Adding some useful mmatrix functions
Doing a bit of work on integration.

\documentclass[12pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}

@@

\newtheorem{theorem}{Theorem}[section]

@@

\DeclareMathOperator{\Dim}{Dim}
\DeclareMathOperator{\Ident}{I}
%\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
%\newcommand{\mmult}[1]{\underset{#1}{\times}}
\newcommand{\mmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\times}$}}}

@@

@@

@@

Maybe... well look at it this way. $F(X)$ is a function which produces some,
afine-like transformation multimatrix for multimatricies of shape $|X|$,
since it must have a right hand shape of $\ldots \oplus |X|$. This integration
occures over a linear path of $X$ as it moves from $A$ to $B$ applying that
transformation and adding up the results of the transformed multimatricies with
a weight proportional to the step size.

So, it's sort of like a line integral but not really. They're related somehow.
\end{document}

>>>>

\documentclass[12pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{pdflscape}

@@

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[theorem]

@@

\DeclareMathOperator{\Dim}{Dim}
\DeclareMathOperator{\Ident}{I}
\DeclareMathOperator{\Tran}{Tran}
%\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
%\newcommand{\mmult}[1]{\underset{#1}{\times}}
\newcommand{\mmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\times}$}}}

@@

\begin{definition}[Multimatrix Subtractin]
\[ A - B = A + (-1)B \]
\end{definition}

@@

\subsection{Transposition}

\begin{definition}[Multimatrix Transposition]
Let $|X| = \vec{l} \oplus \vec{r}$ where $|\vec{l}| = l$ and $|\vec{r}| = r$
\[ |\Tran(X, l)| = \vec{r} \oplus \vec{l} \]
And,
\[ \forall \bar{l} \in \Dim(\vec{l}), \bar{r} \in \Dim(\vec{r}) : \]
\[ \Tran(X, l)[\bar{r} \oplus \bar{l}] = X[\bar{l} \oplus \bar{r}] \]
\end{definition}

\section{Derivative Rules}

\begin{theorem}[Right Multiplicative Derivative]
\[ \frac{d(A \mmult{n} X)}{dX} = A \mmult{n} \Ident^2(|X|) \]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\begin{theorem}[Left Multiplicative Derivative]
\[ \frac{d(X \mmult{n} A)}{dX} = \Ident^2(|X \mmult{n} A|) \mmult{n} \Tran(A, n) \]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\begin{theorem}[Transpose Derivative]
$|X| = \vec{l} \oplus \vec{r}$
\[
 \frac{d\Tran(X, |\vec{l}|)}{dX} =
 \Tran(\Ident^2(\vec{r}) \mmult{0} \Ident^2(\vec{l}), |\vec{r}|)
\]
\end{theorem}
\begin{proof}
\begin{align*}
 \frac{d\Tran(X, |\vec{l}|)}{dX}
 [\bar{r_1} \oplus \bar{l_1} \oplus \bar{l_2} \oplus \bar{r_2}]
 &= \delta_{\bar{r_1}\bar{r_2}} \delta_{\bar{l_1}\bar{l_2}} \\
 &= \delta_{\bar{r_2}\bar{r_1}} \delta_{\bar{l_1}\bar{l_2}} \\
 &=
  \Ident^2(|\vec{r}|)[\bar{r_2}\oplus\bar{r_1}]
  \Ident^2(|\vec{l}|)[\bar{l_1}\oplus\bar{l_2}] \\
 &=
 	\left(
		\Ident^2(|\vec{r}|)
		\mmult{0}
		\Ident^2(|\vec{l}|)
	\right)
	[\bar{r_2}\oplus\bar{r_1}\oplus\bar{l_1}\oplus\bar{l_2}] \\
 &=
  \Tran(
    \Ident^2(|\vec{r}|)
	  \mmult{0}
    \Ident^2(|\vec{l}|)
  , |\vec{r}|) 
 [\bar{r_1} \oplus \bar{l_1} \oplus \bar{l_2} \oplus \bar{r_2}]
\end{align*}
\end{proof}

\begin{theorem}[Addition Rule]
\[ \frac{d(F(X) + G(X))}{dX} = \frac{dF(X)}{dX} + \frac{dG(X)}{dX} \]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\begin{theorem}[Scalar Multiplication Rule]
\[ \frac{d(sF(X))}{dX} = s\frac{dF(X)}{dX} \]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\begin{landscape}
\begin{theorem}[Multiplication Rule]
Let $|F| = \vec{f} \oplus \vec{c}$, $|G| = \vec{c} \oplus \vec{g}$,
and $|X| = \vec{x}$. Then,
\begin{align*}
 \frac{d\left(F(X) \mmult{|\vec{c}|} G(X)\right)}{dX} =
 F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} +
 \Tran\left(
   \Tran(G(X), |\vec{c}|)
	   \mmult{|\vec{c}|}
	 \Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right),
   |\vec{g} \oplus \vec{x}|
 \right)
\end{align*}
\end{theorem}
\begin{proof}
\[
 \forall
  \bar{f} \in \Dim(\vec{f}),
	\bar{g} \in \Dim(\vec{g}),
	\bar{x} \in \Dim(\vec{x})
 :
\]
\begin{align*}
 \frac{d\left(F(X) \mmult{|\vec{c}|} G(X)\right)}{dX}
  [\bar{f} \oplus \bar{g} \oplus \bar{x}]
 &= \frac{
 			\partial \left(F(X) \mmult{|\vec{c}|} G(X)\right)[\bar{f} \oplus \bar{g}]
		}{
 			\partial X[\bar{x}]
		} \\
 &= \frac{
 			\partial \left(
				\sum_{\forall \bar{c} \in \Dim(\vec{c})}
				 F(X)[\bar{f} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{g}]
			\right)
		}{
 			\partial X[\bar{x}]
		} \\
 &= \sum_{\forall \bar{c} \in \Dim(\vec{c})}
    \frac{
			\partial F(X)[\bar{f} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{g}]
		}{
		  \partial X[\bar{x}]
	  }\\
 &= \sum_{\forall \bar{c} \in \Dim(\vec{c})}
		F(X)[\bar{f} \oplus \bar{c}]
    \frac{\partial G(X)[\bar{c} \oplus \bar{g}]}{\partial X[\bar{x}]}
		+
    \frac{\partial F(X)[\bar{f} \oplus \bar{c}]}{\partial X[\bar{x}]}
		G(X)[\bar{c} \oplus \bar{g}] \\
 &=
	 \left(
		\sum_{\forall \bar{c}}
			F(X)[\bar{f} \oplus \bar{c}]
			\frac{\partial G(X)[\bar{c} \oplus \bar{g}]}{\partial X[\bar{x}]}
	 \right)
	 +
	 \left(
		\sum_{\forall \bar{c}}
			\frac{\partial F(X)[\bar{f} \oplus \bar{c}]}{\partial X[\bar{x}]}
			G(X)[\bar{c} \oplus \bar{g}]
	 \right) \\
 &=
 	 l + r
\end{align*}
\begin{align*}
 l
 &=
	\sum_{\forall \bar{c}}
		F(X)[\bar{f} \oplus \bar{c}]
		\frac{\partial G(X)[\bar{c} \oplus \bar{g}]}{\partial X[\bar{x}]} \\
 &=
	\sum_{\forall \bar{c}}
		F(X)[\bar{f} \oplus \bar{c}]
		\frac{dG(X)}{dX}[\bar{c} \oplus \bar{g} \oplus \bar{x}] \\
 &=
	 \left( F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} \right)
	 [\bar{f} \oplus \bar{g} \oplus \bar{x}]
\end{align*}
\begin{align*}
 r
 &=
	\sum_{\forall \bar{c}}
		\frac{\partial F(X)[\bar{f} \oplus \bar{c}]}{\partial X[\bar{x}]}
		G(X)[\bar{c} \oplus \bar{g}] \\
 &=
	\sum_{\forall \bar{c}}
		\frac{dF(X)}{dX}[\bar{f} \oplus \bar{c} \oplus \bar{x}]
		G(X)[\bar{c} \oplus \bar{g}] \\
 &=
	\sum_{\forall \bar{c}}
		\Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
			[\bar{c} \oplus \bar{x} \oplus \bar{f}]
		\Tran(G(X), |\vec{c}|)[\bar{g} \oplus \bar{c}] \\
 &=
	\sum_{\forall \bar{c}}
		\Tran(G(X), |\vec{c}|)[\bar{g} \oplus \bar{c}]
		\Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
			[\bar{c} \oplus \bar{x} \oplus \bar{f}] \\
 &=
  \left(
		\Tran(G(X), |\vec{c}|) \mmult{|\vec{c}|}
		\Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
	\right)[\bar{g} \oplus \bar{x} \oplus \bar{f}] \\
 &= 
  \Tran\left(
		\Tran(G(X), |\vec{c}|) \mmult{|\vec{c}|}
		\Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
		, |\vec{g} \oplus \vec{x}|
	\right)[\bar{f} \oplus \bar{g} \oplus \bar{x}]
\end{align*}
Therefore 
\[
 \frac{d\left(F(X) \mmult{|\vec{c}|} G(X)\right)}{dX}
  [\bar{f} \oplus \bar{g} \oplus \bar{x}]
\]
\begin{align*}
	=& 
	\left( F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} \right)
	[\bar{f} \oplus \bar{g} \oplus \bar{x}] \\
	&+
  \Tran\left(
		\Tran(G(X), |\vec{c}|) \mmult{|\vec{c}|}
		\Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
		, |\vec{g} \oplus \vec{x}|
	\right)[\bar{f} \oplus \bar{g} \oplus \bar{x}] \\
\end{align*}
\[
	=
  \left\{
		\left( F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} \right)
		+
		\Tran\left(
			\Tran(G(X), |\vec{c}|) \mmult{|\vec{c}|}
			\Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
			, |\vec{g} \oplus \vec{x}|
		\right)
	\right\}
	[\bar{f} \oplus \bar{g} \oplus \bar{x}]
\]
\end{proof}
\end{landscape}

\subsection{Chain Rules}

@@

Maybe... well look at it this way. $F(X)$ is a function which produces some,
afine-like transformation multimatrix for multimatricies of shape $|X|$,
since it must have a right hand shape of $\ldots \oplus |X|$. This integration
occures over a linear path of $X$ as it moves from $A$ to $B$ applying that
transformation and adding up the results of the transformed multimatricies with
a weight proportional to the step size... and in the direction of the step.

So, it's sort of like a line integral but not really. They're related somehow.

\begin{landscape}
Let's see if I can prove that theory,
\begin{theorem}[Fundamental Rule of Multimatrix Calculus]
Let $G(X) = \int_A^X F(Y) dY$ then $dG(X)/dX = F(X)$.
\end{theorem}
\begin{proof}
\begin{align*}
	G(X)
	&= \int_A^X F(Y) dY \\
	&= 
		\lim_{n \to \infty}
	 	\sum_{i=1}^n
		  F\left(A+\frac{i}{n}(X-A)\right)
		  \mmult{||Y||}
		  \left(\frac{X-A}{n}\right)
\end{align*}
\begin{alignat*}{3}
	\frac{dG(X)}{dX}
	&=&&
	  \frac{
			d \left\{
			\lim_{n \to \infty}
			\sum_{i=1}^n
				F\left(A+\frac{i}{n}(X-A)\right)
				\mmult{||Y||}
				\left(\frac{X-A}{n}\right)
			\right\}
		}{dX} \\
	&=&&
		\lim_{n \to \infty}
		\frac{
			d \left\{
			\sum_{i=1}^n
				F\left(A+\frac{i}{n}(X-A)\right)
				\mmult{||Y||}
				\left(\frac{X-A}{n}\right)
			\right\}
		}{dX} \\
	&=&&
		\lim_{n \to \infty}
		\sum_{i=1}^n
			\frac{
				d \left\{
					F\left(A+\frac{i}{n}(X-A)\right)
					\mmult{||Y||}
					\left(\frac{X-A}{n}\right)
				\right\}
			}{dX} \\
	&=&&
		\lim_{n \to \infty}
			\sum_{i=1}^n
				F\left(A+\frac{i}{n}(X-A)\right)
					\mmult{||Y||}
					\frac{d \left(\frac{X-A}{n}\right)}{dX}
				\\&&&+
				\Tran\left(
					\Tran\left(\frac{X-A}{n}, ||Y||\right)
					\mmult{||Y||}
					\Tran\left(\frac{
						d \left\{F\left(A+\frac{i}{n}(X-A)\right)\right\}
					}{dX}, |\vec{f}|\right),
					|\vec{x} \oplus \vec{x}|
				\right) \\
	&=&&
		\lim_{n \to \infty}
			\sum_{i=1}^n
				F\left(A+\frac{i}{n}(X-A)\right)
					\mmult{||Y||}
					\frac{1}{n}\Ident^2(|X|)
				\\&&&+
				\Tran\left(
					\frac{X-A}{n}
					\mmult{||Y||}
					\Tran\left(
						\frac{dF(X)}{dX}
						\mmult{|X|}
						\frac{i}{n}\Ident^2(|X|), |\vec{f}|\right),
					|\vec{x} \oplus \vec{x}|
				\right) \\
	&=&&
		\lim_{n \to \infty}
			\sum_{i=1}^n
				\frac{1}{n}F\left(A+\frac{i}{n}(X-A)\right)
				\\&&&+
				\Tran\left(
					\frac{X-A}{n}
					\mmult{||Y||}
					\Tran\left(
						\frac{i}{n}\frac{dF(X)}{dX}
						, |\vec{f}|\right),
					|\vec{x} \oplus \vec{x}|
				\right)
\end{alignat*}
At this point I'm fairly stuck.
\end{proof}
\end{landscape}
\end{document}
